### 2021-02-25 yfcc100m/paper/vldb2021/eval.tex
Add reference to other results
Update Comparison systems figures and eval description

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/comparison_system}
\caption{Comparison Systems: Logical view of the interaction between the client application with VDMS (left) and the baseline systems (right). The baseline systems are either based on MySQL or PostgreSQL for operating and querying metadata.}
\label{fig:systems}
\end{figure*}

@@

Given that there are no other open-source systems that provide similar
functionality and interfaces as VDMS, we have implemented two equivalent
visual data management system as baselines, comprised of a combination of
widely available, off-the-shelf components.
The first baseline uses MySQL Server 5.7 (for storing metadata),
Apache Web Server 2.4.18 (as interface for image access), and
OpenCV 3.3 (to provide pre-processing operations on images).
The other baseline system replaces the MySQL Server 5.7 with the
most advanced open source relational database, PostgreSQL 9.5 \cite{postgresql}.
We decided to use relational databases in the baseline systems instead of
non-relational databases because~\cite{Jatana2012, li_2019}:

@@

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/comparison_system}
\caption{Comparison Systems: Logical view of the interaction between the client application with VDMS (left) and the baseline systems based on Apache Web Server and PostgreSQL (middle), or MySQL (right). The image repository is shared.}
\label{fig:systems}
\end{figure*}

@@

Given that there are no other open-source systems that provide similar
functionality and interfaces as VDMS (i.e., transactionally dealing with images
and metadata behind a single interface), we have implemented two equivalent
visual data management system as baselines, comprised of a combination of
widely available, off-the-shelf components.
The first baseline uses MySQL Server 5.7 (for storing metadata),
Apache Web Server 2.4.18 (as interface for image access), and
OpenCV 3.3 (to provide pre-processing operations on images).
The other baseline system replaces the MySQL Server 5.7 with a
most advanced open-source relational database, PostgreSQL 9.5 \cite{postgresql}.
We decided to use relational databases in the baseline systems instead of
non-relational databases because of their madurity, and also because it is
the most common tools used for storing and querying metadata
~\cite{Jatana2012, li_2019}:

@@

Because of space constraints, we are only showing a subset of our evaluation.

We are making available the all available  of For more details about our comprehensive evaluation.
available
\footnote{https://github.com/luisremis/visual\_storm/tree/master/yfcc100m/python/eval/results}
% TODO. Upload the final version of the plots once we are sure we are not making
% more modifications.
